---
title: ' Dashboard'
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(ggvis)
```


```{r}
#install.packages("Rtools")
getOption("repos")
```


```{r}
install.packages()
```

```{r}
packageurl <- "https://cran.r-project.org/src/contrib/Archive/xfun/"
install.packages(packageurl, repos=NULL, type="source")

```

## Set up

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(shiny)
library(shinydashboard)
```

## Set up

```{r setup}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(shiny)
library(shinydashboard)
```

## Is important so we can think about what information we want our users to gain from our dashboard.

```{r EDA}

# the solutions will use "thebeatles" dataset
artist_name <- "thebeatles"
# Read in
#getwd()
#df<- read.csv('https://raw.githubusercontent.com/anastasia-lucas/rladies_shinydashboards/main/data/queen_lyrics.txt')

df<- queen_lyrics
##df <- read.delim(paste0("data/", artist_name, "_lyrics.txt"))
head(df)
str(df)
```

```{r}
library(dplyr)
library(tidyr)
library(stringr)

#library(readr)
#df <- read_csv("Final/queen_lyrics.csv")
#View(df)
#download.file(df)
##import the data in a dataframe
#df %>% separate(x=c('track_title', 'word','album','n'))
##Rename the columns
#colnames(df)< -c("track_title",
 #        "word",
#         "album",
  #       "n")

```

So we have a dataframe with 4 columns. In a sentnce, each row represents the `n` times that a `word` appears in each `track_title` per `album` in our dataset.\
The important thing to remember is that the lyrics are summed across the songs, not across all of the albums.

## Try the most basic dashboard...

i.e. a blank dashboard

```{r basic app}

ui <- dashboardPage(
  dashboardHeader(),
  dashboardSidebar(),
  dashboardBody()
)

server <- function(input, output) {  }
 # note we have defined an input and output that we don't do anything with!

shinyApp(ui, server)
```

### Let's give our app a title and set up a grid layout for our plots

We will use the `fluidPage()` page to create a fluid page layout, i.e. one that will resize to the width of our screen. A fluid page layout consists of fluid rows, created with `fluidRow()` which in turn consist of columns created by the `column()` function. Finally, we can store our app in a `box()` within the column.\
For now, we will create a dashboard with one row and one column with space for one plot. The layout will be specified in the UI section of the app.\
Try filling in the blanks to specify the width and title.

##1########################################################################## 

```{r }

ui <- dashboardPage( skin='red',
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(
    sliderInput("bins", "Number of Breaks", 1,100,50),
      sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        
        menuSubItem("Home Page", tabName = "Home"),
        menuSubItem("Sales", tabName = "Sales"),
        menuItem("Raw Data", tabName = "RawData"),
        sliderInput(inputId = "range1",
                    label = "Data Range",
                    min = 1,
                    max = 31,
                    value = c(1,31))
      )),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL) 
              )
      )
    )
  )
)

server <- function(input, output) {  }
 # note we have defined an input and output that we don't do anything with!

shinyApp(ui, server)

```

####1####################################################################### 

```{r exercise 1}

ui <- dashboardPage(
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL) 
              )
      )
    )
  )
)

server <- function(input, output) {  }
 # note we have defined an input and output that we don't do anything with!

shinyApp(ui, server)
```

### Make a bar chart that displays the count of the top 10 most frequent words summed across all albums

Our plot will be rendered in the server section of our app using the following code`output$plot1 <- renderPlot({# ploting goes here})`. We have already added the plot output in the UI section and we will refer to the plot using the same outputID as we did in the `plotOutput` function, "plot1".\
Some other common output functions are `tableOutput`, `dataTableOutput`, `plotlyOutput`, & `textOutput`, which we will take a look at later.\
Hint: the code to create a regular `ggplot` with the top 10 most frequent words summed across all albums is shown below.

```{r hint 1}
df %>% 
  # Summarize
  group_by(word) %>% 
  summarise(occurrences=sum(n)) %>% 
  arrange(desc(occurrences)) %>% 
  top_n(10) %>%
  ungroup() %>%
  # Start plotting with ggplot
  ggplot(aes(x=word, 
             y=occurrences)) +
   geom_col() +
   ## Bonus: uncomment to make some aesthetic changes or add your own
   ylab("count") +
   coord_flip() +
   theme_minimal() +
   scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
   ggtitle(paste("Top", 10, "frequently used words")) + 
   geom_blank()

```

##2 ################################################################################## 

```{r}
ui <- dashboardPage( skin='red',
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(
    sliderInput("bins", "Number of Breaks", 1,100,50),
      sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        
        menuSubItem("Home Page", tabName = "Home"),
        menuSubItem("Sales", tabName = "Sales"),
        menuItem("Raw Data", tabName = "RawData"),
        sliderInput(inputId = "range1",
                    label = "Data Range",
                    min = 1,
                    max = 31,
                    value = c(1,31))
      )),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL) 
              )
      )
    )
  )
)
server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", 10, "frequently used words")) + 
    geom_blank()
  })
}

shinyApp(ui, server)

```

################################################################################## 

```{r exercise 2}

ui <- dashboardPage(
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      )
    )
  )
)

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", 10, "frequently used words")) + 
    geom_blank()
  })
}

shinyApp(ui, server)
```

### Now let's make it reactive!

We can create one of the control widgets that we saw earlier in our UI. This will allow the user to select the number of words to display.\
Fill in the blanks to create a `numericInput()` in our `box()` with the following parameters:\
`inputId` which is used to access the value is `inputId = "select_topn"`\
`label` displayed on the widget is `label = Select number of words to display`\
`min` value user can select is `min = 3`\
`max` value user can select is `max = 20`\
default `value` to display is `value = 10`\
Since it only makes sense to select whole numbers here, we should also set `step = 1`\
Once we have our input set up, we need to refer to it in our `server()` function when we render the plot.\
Hint: We can extract the user value using our inputId `input$select_topn`

###3###################################################################### 

```{r}
ui <- dashboardPage( skin='red',
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(
    sliderInput("bins", "Number of Breaks", 1,100,50),
      sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        
        menuSubItem("Home Page", tabName = "Home"),
        menuSubItem("Sales", tabName = "Sales"),
        menuItem("Raw Data", tabName = "RawData"),
        sliderInput(inputId = "range1",
                    label = "Data Range",
                    min = 1,
                    max = 31,
                    value = c(1,31))
      )),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   numericInput(inputId = "select_topn",
                                label = "Select number of words to display", 
                                value = 10, min = 3, max = 20, step=1),
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL) 
              )
      )
    )
  )
)
server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
}

shinyApp(ui, server)



```

################################################################## 

```{r exercise 3}

ui <- dashboardPage(
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   numericInput(inputId = "select_topn", 
                                label = "Select number of words to display", 
                                value = 10, min = 3, max = 20, step=1),
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      )
    )
  )
)

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
}

shinyApp(ui, server)
```

### Let's try to show this information in table format

We can use Shiny's `dataTableOutput()` function for this. We can put this table in its own column such that the dashboard has two columns, each containing one box, within the fluid row.\
If we were making a production ready dashboard, we probably would *not* want to have multiple graphs/tables that show the same information, but we can use it here as a proof of concept. Try to fill the blanks below to add the widths and the dataframe that should be displayed as a table.\
Hint: We will need to divide the width of our boxes by 2 if we want to give both apps equal billing.

######4#################################################################


```{r}


ui <- dashboardPage( skin='red',
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(
    sliderInput("bins", "Number of Breaks", 1,100,50),
      sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        
        menuSubItem("Home Page", tabName = "Home"),
        menuSubItem("Sales", tabName = "Sales"),
        menuItem("Raw Data", tabName = "RawData"),
        sliderInput(inputId = "range1",
                    label = "Data Range",
                    min = 1,
                    max = 31,
                    value = c(1,31))
      )),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=12,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   numericInput(inputId = "select_topn",
                                label = "Select number of words to display", 
                                value = 10, min = 3, max = 20, step=1),
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL) 
              ),
        column(# width should be between 1 and 12
               width=6,
               box(dataTableOutput("table1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                 
               )
        )
      )
    )
  )
)
             
     

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
  
  output$table1 <- renderDataTable({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup()
  })
}

shinyApp(ui, server)





```

##########################################################################


```{r exercise 4}

ui <- dashboardPage(
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=6,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   numericInput(inputId = "select_topn", 
                                label = "Select number of words to display", 
                                value = 10, min = 3, max = 20, step=1),
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              ),
        column(# width should be between 1 and 12
               width=6,
               box(dataTableOutput("table1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      
      )
    )
  )
)

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
  
  output$table1 <- renderDataTable({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup()
  })
}

shinyApp(ui, server)
```

Similarly we could add additional fluid rows with variable numbers of columns to create more complicated layouts. You can also explicitly set the height and width for each of the boxes.

### But this creates a problem for our users...

It's not obvious that the input widget controls both the chart and the table. It might be more apparent if we move the input control widget to the sidebar.\
To do this, we can simply move our `numericInput()` function inside of `dashboardSidebar()`.

###5###################################################################


```{r}
ui <- dashboardPage( skin='red',
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(
    sliderInput("bins", "Number of Breaks", 1,100,50),
      sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        
        menuSubItem("Home Page", tabName = "Home"),
        menuSubItem("Sales", tabName = "Sales"),
        menuItem("Raw Data", tabName = "RawData"),
        sliderInput(inputId = "range1",
                    label = "Data Range",
                    min = 1,
                    max = 31,
                    value = c(1,31)),
        numericInput(inputId = "select_topn", 
                 label = "Select the number of words to display", 
                 value = 10, min = 3, max = 20, step=1)
      )),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=6,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              ),
        column(# width should be between 1 and 12
               width=6,
               box(dataTableOutput("table1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      )
    )
  )
)

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
  
  output$table1 <- renderDataTable({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup()
  })
}

shinyApp(ui, server)

```

####################################################################

```{r exercise 5}

ui <- dashboardPage(
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(  
    numericInput(inputId = "select_topn", 
                 label = "Select the number of words to display", 
                 value = 10, min = 3, max = 20, step=1)
  ),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=6,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              ),
        column(# width should be between 1 and 12
               width=6,
               box(dataTableOutput("table1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      )
    )
  )
)

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
  
  output$table1 <- renderDataTable({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(input$select_topn) %>%
    ungroup()
  })
}

shinyApp(ui, server)
```

Note that we could also create a seperate box for our control widget(s) inside of the dashboard body.

### Try to change the type of the control widget input from `numericInput` to `textInput`.

We can use `?textInput` to see the parameters we need to set.\
Hint: We won't need `min`, `max`, or `step` values here.

#########6#############################################################


```{r}
ui <- dashboardPage( skin='red',
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(
    numericInput(inputId = "select_topn", 
                 label = "Select the number of words to display", 
                 value = 10, min = 3, max = 20, step=1),
    
    #sliderInput("bins", "Number of Breaks", 1,100,50),
      sidebarMenu(
        menuItem("Dashboard", tabName = "dashboard", icon = icon("dashboard")),
        
        menuSubItem("Home Page", tabName = "Home"),
        menuSubItem("Sales", tabName = "Sales"),
        menuItem("Raw Data", tabName = "RawData"),
        sliderInput(inputId = "range1",
                    label = "Data Range",
                    min = 1,
                    max = 31,
                    value = c(1,31))
        #numericInput(inputId = "select_topn", 
         #        label = "Select the number of words to display", 
          #       value = 10, min = 3, max = 20, step=1)
      )),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=6,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              ),
        column(# width should be between 1 and 12
               width=6,
               box(dataTableOutput("table1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      )
    )
  )
)


server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(as.integer(input$select_topn)) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
  
  output$table1 <- renderDataTable({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(as.integer(input$select_topn)) %>%
    ungroup()
  })
}

shinyApp(ui, server)

```



###############################################################################33
```{r exercise 6}

ui <- dashboardPage(
  dashboardHeader(title = "Song Lyrics"),
  dashboardSidebar(  
    textInput(inputId = "select_topn", 
              label = "Select the number of words to display", 
              value = 10)
  ),
  dashboardBody(    
    fluidPage(
      fluidRow(
        column(# width should be between 1 and 12
               width=6,
               box(plotOutput("plot1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              ),
        column(# width should be between 1 and 12
               width=6,
               box(dataTableOutput("table1"), 
                   title="Most Common Words Across Albums",
                   # For column based layouts, we can set box width to NULL
                   # This overrides the default value
                   width=NULL)
              )
      )
    )
  )
)

server <- function(input, output) { 
  output$plot1 <- renderPlot({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(as.integer(input$select_topn)) %>%
    ungroup() %>%
    ggplot(aes(x=word, 
               y=occurrences)) +
    geom_col() +
    ## Bonus: uncomment to make some aesthetic changes or add your own
    ylab("count") +
    coord_flip() +
    theme_minimal() +
    scale_fill_gradient(high = "#f6a97a", low="#ca3c97") +
    ggtitle(paste("Top", input$select_topn, "frequently used words")) + 
    geom_blank()
  })
  
  output$table1 <- renderDataTable({
    df %>% 
    group_by(word) %>% 
    summarise(occurrences=sum(n)) %>% 
    arrange(desc(occurrences)) %>% 
    top_n(as.integer(input$select_topn)) %>%
    ungroup()
  })
}

shinyApp(ui, server)
```

```{r}
library(rsconnect)
deployApp()

```

```{r}
install.packages("remotes")
remotes::install_github("rstudio/rsconnect")
```